\huge Tor's Usability for Censorship Circumvention

### 2016-04-26 pets2017-paper/pets2017-paper.tex
fix spelling error

\section {Acknowledgments}
I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

>>>>

\section {Acknowledgments}
I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
